Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-06-21 prop_letter.tex
prop_letter.tex Updated...

According to Mermin's comment\nb\cite{Mermin1999},
\begin{quote}
...although the outcomes deduced from such imperfect measurements
will occasionally differ dramatically from those allowed in the ideal
case, if the misalignment is very slight, the statistical distribution
of outcomes will differ only slightly from the ideal case...
\end{quote}
if the imperfection of the measurement is small enough, the finitely
precise measurement should not nullify the Kochen-Specker theorem.
This idea can be modeled precisely by QIVPMs.

\begin{definition}\label{def:delta-deterministic}An interval-valued
probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
is called $\left(1/n,\delta\right)$-deterministic if for every $\left[\ell,r\right]\in\mathscr{I}$,
there is a $k\in\mathbb{Z}$ such that $\left[\ell,r\right]\subseteq\left[k/n-\delta,k/n+\delta\right]$.\end{definition}

For example, any cryptodeterministic QIVPM is $\left(1,0\right)$-deterministic.
For another example, given a three-dimensional Hilbert space, 
\begin{equation}
\iota_{\infty}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} 
\end{equation}
is $\left(1,\frac{1}{3}\right)$-deterministic and $\left(\frac{1}{3},0\right)$-deterministic,
where $\iota_{\infty}\left(x\right)=\left[x,x\right]$. However, we
will prove there is generally no $\left(1/n,\delta\right)$-deterministic
probability measures when $\delta$ is much smaller than $1/n$.

\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
and a quantum $\left(1/n,\delta\right)$-deterministic probability
measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$ with $\delta<1/\left(3n\right)$,
if $\bar{\mu}(P)\subseteq\left[k/n-\delta,k/n+\delta\right]$, let
$\mu(P)=k/n$, then $\mu:\events\rightarrow\left[0,1\right]$ is a
quantum probability measure. In another word, $\iota_{\infty}\circ\mu$
is $\left(1/n,0\right)$-deterministic.\end{lemma}

\begin{proof} The essential part to verify $\mu$ is a quantum probability
measure is to verify Eq.~(\ref{eq:QuantumProbability-Addition}). Given a pair of orthogonal
operators\nb$P_{0}$ and $P_{1}$, let $\pmeas\left(P_{0}\right)=k_{0}/n$ and $\pmeas\left(P_{1}\right)=k_{1}/n$.
Then, 
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{k_{0}+k_{1}}{n}-2\delta,\frac{k_{0}+k_{1}}{n}+2\delta\right]\,.
\end{equation}
Since $\delta<1/\left(3n\right)$, we have
\begin{subequations}
\begin{eqnarray}
\frac{k_{0}+k_{1}-1}{n}+\delta&<&\frac{k_{0}+k_{1}}{n}-2\delta\\
\frac{k_{0}+k_{1}}{n}+2\delta&<&\frac{k_{0}+k_{1}+1}{n}-\delta\,.
\end{eqnarray}
\end{subequations}
The previous inequalities imply that if $\bar{\mu}\left(P_{0}+P_{1}\right)$
overlap with any interval of the form $\left[k/n-\delta,k/n+\delta\right]$
for some $k$, $k$ must be $k_{0}+k_{1}$, i.e., 
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{k_{0}+k_{1}}{n}-\delta,\frac{k_{0}+k_{1}}{n}+\delta\right]\,.
\end{equation}
Therefore, 
\begin{equation}
\pmeas\left(P_{0}+P_{1}\right)=\frac{k_{0}+k_{1}}{n}=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\,.
\end{equation}
\end{proof}

Together with the Kochen-Specker theorem, we will have the following
corollary.

\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension\nb$d\ge3$, there is no quantum $\left(1,\delta\right)$-deterministic
probability measure for $\delta<\frac{1}{3}$.\end{cor}

In general~\cite{Redhead1987-REDINA}, Gleason's theorem asserts
that a quantum probability measure must be continuous. Therefore,
a $\left(1/n,0\right)$-deterministic QIVPM exists if and only if
$d\mid n$, and so does a $\left(1/n,\delta\right)$-deterministic
QIVPM for $\delta<1/\left(3n\right)$.

>>>>

According to Mermin's comment\nb\citep{Mermin1999}, 
\begin{quote}
...although the outcomes deduced from such imperfect measurements
will occasionally differ dramatically from those allowed in the ideal
case, if the misalignment is very slight, the statistical distribution
of outcomes will differ only slightly from the ideal case... 
\end{quote}
if the imperfection of the measurement is small enough, the finitely
precise measurement should not nullify the Kochen-Specker theorem.
This idea can be modeled precisely by considering the following kind
of QIVPMs.

\begin{definition}\label{def:delta-deterministic}An QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
is called $\delta$-deterministic if either $\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]$
or $\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]$ for
any $P\in\events$.\end{definition}

For example, any cryptodeterministic QIVPM is $0$-deterministic.
For another example, given a three-dimensional Hilbert space, a $\frac{1}{3}$-deterministic
QIVPM can be given by $\bar{\mu}\left(P\right)=\left[x,x\right]$,
where $P$ projects onto a $x$-dimensional subspace. By utilizing
$\delta$-deterministic QIVPMs, we can have a Kochen-Specker theorem
with finite precision measurement.

\begin{thm}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension\nb$d\ge3$, there is no $\delta$-deterministic QIVPM
for $\delta<\frac{1}{3}$.\end{thm}

\begin{proof}Suppose there is a $\delta$-deterministic QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$,
then we can define a cryptodeterministic QIVPM\nb$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{ \imposs,\necess\right\} $
by 
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
\end{cases}
\end{equation}

The essential part to verify $\bar{\mu}^{\textrm{D}}$ is a cryptodeterministic
QIVPM is to verify\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs\\
 & \Rightarrow & \bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs
\end{eqnarray}
\end{subequations}for orthogonal operators\nb$P_{0}$ and $P_{1}$
which is a special case of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).

When $\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have $\bar{\mu}\left(P_{0}\right)\subseteq\left[0,\delta\right]$
and $\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
implies $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
Since $\delta<\frac{1}{3}\Rightarrow2\delta<1-\delta$, $\bar{\mu}\left(P_{0}+P_{1}\right)$
cannot be a subset of $\left[1-\delta,1\right]$, but $\bar{\mu}\left(P_{0}+P_{1}\right)$
is a subset of either $\left[0,\delta\right]$ or $\left[1-\delta,1\right]$.
Hence, $\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of $\left[0,\delta\right]$,
which implies $\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$.
The remain part of the proof are routine verification.\end{proof}
